Are We Teaching Cybersecurity (and how well)?\\(Abstract 20 January, Paper 27th)

### 2019-01-16 ITiCSE2019.tex
Added Parrishetal2018a

\begin{abstract}
There are many facets to CyberSecurity education: we address the questions ``what should the generalist computer scientist know'' and ``how well is that being taught''. We consider particularly the UK perspective, where the British Computer Society accredits computing degrees, and insists on a certain CyberSecurity element in all such.
\end{abstract}

@@

There are calls for education to respond to this situation, which it does both at the individual level and via recommended curricula \cite{ACM2013a} and professional accreditation requirements \cite{BCS2018a}.

>>>>

\def\IntroYear{2014}  % when BCS started asking for CyberSecurity
\begin{abstract}
There are many facets to CyberSecurity education: we address the questions ``what should the generalist computer scientist know'' and ``how well is that being taught''. We consider particularly the UK perspective, where the British Computer Society accredits computing degrees, and (since \IntroYear) insists on a certain CyberSecurity element in all such.
\end{abstract}

@@

There are calls for education to respond to this situation, which it does both at the individual level and via recommended curricula \cite{ACM2013a} and professional accreditation requirements \cite{BCS2018a}. There has been a recent international working group \cite{Parrishetal2018a}, but this has yet to report.
